The GWR Smoke's effect on Oregon 2013 Medication of Beta-2 agonists

### 2017-08-08 r_scripts/analysis/oregon_medication.Rmd
Update oregon_medication.Rmd

```{r input category, echo = FALSE, message=FALSE, warning=FALSE}
df_list <- list(asthma_df, copd_df, both_df, other_df)

# create an empty list to row bind dataframes together
datalist_dml <- list()

# datalist_dml[[i]] <- data.frame(df_list[i]) %>%
  asthma_dml <- asthma_df %>%
  left_join(or_zip_to_county, by = "ZIPCODE") %>%
  left_join(or_pop, by = "county") %>%
  mutate(day = ifelse(weekdays(date) == "Monday" |
                      weekdays(date) == "Tuesday" |
                      weekdays(date) == "Wednesday"|
                      weekdays(date) == "Thursday"|
                      weekdays(date) == "Friday", "weekday",
               ifelse(weekdays(date) == "Saturday" |
                      weekdays(date) == "Sunday", "weekend", NA))) %>%
  mutate(geo_smk_pm10_zip = geo_smk_pm_zip/10,
         geo_smk_pm10_lag1_zip =geo_smk_pm_lag1_zip/10,
         geo_smk_pm10_lag2_zip =geo_smk_pm_lag2_zip/10,
         geo_smk_pm10_lag3_zip =geo_smk_pm_lag3_zip/10,
         geo_smk_pm10_lag4_zip =geo_smk_pm_lag4_zip/10,
         geo_smk_pm10_lag5_zip =geo_smk_pm_lag5_zip/10,
         geo_smk_pm10_lag6_zip =geo_smk_pm_lag6_zip/10,
         geo_smk_pm10_lag7_zip =geo_smk_pm_lag7_zip/10)

asthma_dml$day[which(asthma_dml$date=="2013-05-27")] <- "weekend"
asthma_dml$day[which(asthma_dml$date=="2013-07-04")] <- "weekend"
asthma_dml$day[which(asthma_dml$date=="2013-09-02")] <- "weekend"

datalist_dml[[i]]$day[which(datalist_dml[[i]]$date=="2013-05-27")] <- "weekend"
datalist_dml[[i]]$day[which(datalist_dml[[i]]$date=="2013-07-04")] <- "weekend"
datalist_dml[[i]]$day[which(datalist_dml[[i]]$date=="2013-09-02")] <- "weekend"
}

for(i in 1:4){
  i <- 1

  inhaler_geo_lag <- asthma_dml %>%
  select(159, 160:166) # GWR-method

inhaler_temp_lag <- asthma_dml %>%
  select(93, 150:156) # GWR-method

dml_df <- datalist_dml[[i]]

@@

fit <- clogit(outcome ~ inhaler_geo_lag_B + inhaler_temp_lag_B + strata(personkey), 
              asthma_dml)

>>>>

```{r DLM for disease, }

# set variable list
var_list <- c('respiratory', 'asthma', 'pneumonia',  'acute_bronch', 'copd', 
              'cvd', 'isch_heart_dis', 'arrhythmia', 'heart_failure', 
              'cerbrovas_dis', 'myocardial_infarc', 'broken_arm')

start <- Sys.time()
for(j in var_list) { # begin first loop of variable names (outcomes)

  j <- "broken_arm"
  # standard for statement without parallel computing
  #for(j in 1:length(var_list)){
  read_path <- paste('../data_new/casecrossover/time_strat/or', j, 'may_to_sep_time_strat_casecross.csv', sep='_')
  or_disease <- read_csv(read_path)

  or_disease_df <- data.frame(or_disease)

  or_disease_lag_df <- or_disease_df %>%
  left_join(or_zip_to_county, by = "ZIPCODE") %>%
  left_join(or_pop, by = "county") %>%
  mutate(day = ifelse(weekdays(date) == "Monday" |
                      weekdays(date) == "Tuesday" |
                      weekdays(date) == "Wednesday"|
                      weekdays(date) == "Thursday"|
                      weekdays(date) == "Friday", "weekday",
               ifelse(weekdays(date) == "Saturday" |
                      weekdays(date) == "Sunday", "weekend", NA))) %>%
  mutate(geo_smk_pm10_zip = geo_smk_pm_zip/10,
         geo_smk_pm10_lag1_zip =geo_smk_pm_lag1_zip/10,
         geo_smk_pm10_lag2_zip =geo_smk_pm_lag2_zip/10,
         geo_smk_pm10_lag3_zip =geo_smk_pm_lag3_zip/10,
         geo_smk_pm10_lag4_zip =geo_smk_pm_lag4_zip/10,
         geo_smk_pm10_lag5_zip =geo_smk_pm_lag5_zip/10,
         geo_smk_pm10_lag6_zip =geo_smk_pm_lag6_zip/10,
         geo_smk_pm10_lag7_zip =geo_smk_pm_lag7_zip/10)

or_disease_lag_df$day[which(or_disease_lag_df$date=="2013-05-27")] <- "weekend"
or_disease_lag_df$day[which(or_disease_lag_df$date=="2013-07-04")] <- "weekend"
or_disease_lag_df$day[which(or_disease_lag_df$date=="2013-09-02")] <- "weekend"

which(colnames(or_disease_lag_df)=="geo_smk_pm10_zip") #174
which(colnames(or_disease_lag_df)=="geo_smk_pm10_lag1_zip") #175
which(colnames(or_disease_lag_df)=="wrf_temp_zip") #94
which(colnames(or_disease_lag_df)=="wrf_temp_lag1_zip") #151

or_disease_geo_lag <- or_disease_lag_df %>%
  select(174, 175:181) # GWR-method

or_disease_temp_lag <- or_disease_lag_df %>%
  select(94, 151:157) # GWR-method

lag_max <- 7
n1 <- length(or_disease_geo_lag[,1])
n2 <- length(or_disease_temp_lag[,1])

or_disease_geo_lag <- as.matrix(or_disease_geo_lag)
or_disease_temp_lag <- as.matrix(or_disease_temp_lag)

@@

or_disease_geo_lag_B <- or_disease_geo_lag%*%B
or_disease_geo_lag_B <- or_disease_temp_lag%*%B

fit <- clogit(outcome ~ or_disease_geo_lag_B + or_disease_geo_lag_B + strata(personkey), 
              or_disease_lag_df)
